Trends of SDR in Thessaloniki

### 2023-09-18 Article.Rmd
Commit 2023-09-18 20:14

x_latex <- knitr::kable(LT,
                        format   = "latex",
                        booktabs = T,
                        escape   = T,
                        # format.args = list(digits = 3),
                        linesep  = "",
                        # align    = "ccrr",
                        caption  = "sssssss")
x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c("striped",
                                    "hold_position")
                  )

>>>>

# x_latex <- knitr::kable(LT,
#                         format   = "latex",
#                         booktabs = T,
#                         escape   = T,
#                         # format.args = list(digits = 3),
#                         linesep  = "",
#                         align    = "ccc",
#                         caption  = "test")
# x_latex %>%
#     kable_styling(latex_options = c("hold_position"))
